### 2018-05-13 README.Rmd
update README

```{r, out.width = "60%"}
dt_plot_predictions(predictions, "337", "workers_compensation",
                    "paid_loss")
```

```{r, out.width = "60%"}
dt_plot_predictions(predictions, "337", "workers_compensation",
                    "claims_outstanding")
```

>>>>

```{r, out.width = "60%"}
# devtools::install_github("thomasp85/patchwork")
library(patchwork)
paid_plot <- dt_plot_predictions(predictions, "337", "workers_compensation",
                    "paid_loss")
case_plot <- dt_plot_predictions(predictions, "337", "workers_compensation",
                    "claims_outstanding")
paid_plot + case_plot + plot_layout(ncol = 1)
```

## Testing different architectures

If you would like to try out different architectures or hyperparameters, you can do so by providing a function that returns a compiled keras model. See the source code of `dt_model()` for a template. In order to utilize other functions in this package, the inputs and outputs of your custom function have to match those of `dt_model()`. You can also implement different early stopping criteria by providing a function similar to `dt_optimize_epochs()`.

For more details on the **keras** R package, visit [https://keras.rstudio.com/](https://keras.rstudio.com/).
